---
title: "Merged Notebook"
output: html_document
date: '2022-08-23'


---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


The 2021 half hourly demand, solar and wind generation data has been used to evaluate average solar, wind half hourly capacity factor while the average half hourly demand has been used further for the modelling purpose.

Link to NationalGridESO 2021 half hourly data:  

https://data.nationalgrideso.com/demand/historic-demand-data/r/historic_demand_data_2021


```{r}
library(tidyverse)
library(ggplot2)

maindf <- read_csv("C:/Users/k_gag/OneDrive/Desktop/Dissertation_V2G/Datasets/demanddata_2021.csv")
df <- read_csv("C:/Users/k_gag/OneDrive/Desktop/Dissertation_V2G/Datasets/powersettlement.csv")

df_demand <- read_csv("C:/Users/k_gag/OneDrive/Desktop/Dissertation_V2G/Datasets/halfhourlyavg.csv")

df1 <-df %>% group_by(settlement_period) %>% 
  summarize(halfhourly=mean(capacity))
df1 %>% ggplot(aes(x=))
dfws <- maindf %>% group_by(SETTLEMENT_PERIOD) %>% 
  summarize(halfhourlysolar=mean(EMBEDDED_SOLAR_GENERATION),halfhourlywind=mean(EMBEDDED_WIND_GENERATION),demand=mean(ENGLAND_WALES_DEMAND))
  
df_renewablegen_demand <- read_csv("C:/Users/k_gag/OneDrive/Desktop/Dissertation_V2G/Datasets/halfhourlysolarwind.csv")



```





```{r}

library(tidyverse)
#Vehicle Availiblity Plot

#Fitting points to Lagrange Equation:

df <-data.frame(x = c(0,	0.5,	1,	1.5,	2,	2.5,	3,	3.5,	4,	4.5,	5,	5.5,	6,	6.5,	7,	7.5,	8,	8.5,	9,	9.5,	10,	10.5,	11,	11.5,	12,	12.5,	13,	13.5,	14,	14.5,	15,	15.5,	16,	16.5,	17,	17.5,	18,	18.5,	19,	19.5,	20,	20.5,	21,	21.5,	22,	22.5,	23,	23.5)
,y = c(0.484848484848485,	0.606060606060606,	0.666666666666667,	0.787878787878788,	0.848484848484849,	0.878787878787879,	0.939393939393939,	0.954545454545455,	1,	0.787878787878788,	0.606060606060606,	0.303030303030303,	0.0606060606060606,	0.121212121212121,	0.151515151515152,	0.272727272727273,	0.303030303030303,	0.196969696969697,	0.166666666666667,	0.327272727272727,	0.212121212121212,	0.0909090909090909,	0,	0.0909090909090909,	0.181818181818182,	0.212121212121212,	0.196969696969697,	0.16969696969697,	0.145454545454545,	0.133333333333333,	0.121212121212121,	0.109090909090909,	0.096969696969697,	0.0848484848484848,	0,	0.0757575757575758,	0.181818181818182,	0.303030303030303,	0.424242424242424,	0.378787878787879,	0.351515151515152,	0.227878787878788,	0.181818181818182,	0.16969696969697,	0.145454545454545,	0.109090909090909,	0.0848484848484848,	0.0606060606060606
))

fit5 <- lm(y~poly(x,10,raw=TRUE), data=df)

            
plot(df$x, df$y, pch=19, xlab='x', ylab='y')
x_axis <- seq(1, 24, length=24)
lines(x_axis, predict(fit5, data.frame(x=x_axis)), col='orange', cex=1)
summary(fit5)

```

#Ggplot for the availiblity function

```{r}
library(ggplot2)

ggp <- ggplot(df, aes(x, y)) +    # Create ggplot2 scatterplot
  geom_point()
a1<- ggp +                               # Regression curve & confidence band
  stat_smooth(method = "lm",
              formula = y ~ poly(x, 10))
print(a1 + labs(y = 'Vehicle Availiblity Flux' , x = 'Hours in HH:MM'))

```

```{r}
#Average daily capacity factor for solar and wind:

library(tidyverse)

df_capacity_windsolar <- maindf %>% group_by(SETTLEMENT_PERIOD) %>% 
  summarize(halfhourly_wind=mean(EMBEDDED_WIND_GENERATION),halfhourly_solar=mean(EMBEDDED_SOLAR_GENERATION),capacity_wind=mean(EMBEDDED_WIND_CAPACITY),capacity_solar=mean(EMBEDDED_SOLAR_CAPACITY))

df_capacity_windsolar$deliverypotentialwind =df_capacity_windsolar$halfhourly_wind/df_capacity_windsolar$capacity_wind

df_capacity_windsolar$deliverypotentialsolar =df_capacity_windsolar$halfhourly_solar/df_capacity_windsolar$capacity_solar
```

Regression for Charging at 50% occupancy vs at 80% occupancy based upon the occupancy outputs from the model:
```{r}

library(tidyverse)
library(ggplot2)
df_overall <- read_csv("C:/Users/k_gag/OneDrive/Desktop/Dissertation_V2G/results/overall.csv")

#At 80% compatiblity:

lm80_50 <- lm(formula = Charging_80 ~ Charging_50, data = df_overall)
summary(lm80_50)
plot(lm80_50)

ggplot(data=df_overall, aes(x=Charging_80, y=Charging_50)) + geom_point(color='red') + 
  geom_smooth(method = 'lm', se=FALSE) 

```
```{r}
#LM for 80% vs 30%

lm80_30 <- lm(formula = Charging_80 ~ Charging_30, data = df_overall)
summary(lm80_30)
plot(lm80_30)

ggplot(data=df_overall, aes(x=Charging_80, y=Charging_30)) + geom_point(color='red') + 
  geom_smooth(method = 'lm', se=FALSE) 


```


```{r}

lm50_30 <- lm(formula = Charging_50 ~ Charging_30, data = df_overall)
summary(lm50_30)
plot(lm50_30)

ggplot(data=df_overall, aes(x=Charging_50, y=Charging_30)) + geom_point(color='red') + 
  geom_smooth(method = 'lm', se=FALSE) 

```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
