Primary Notebook:

The 2021 half hourly demand, solar and wind generation data has been used to evaluate average solar, wind half hourly capacity factor while the average half hourly demand has been used further for the modelling purpose.

Link to NationalGridESO 2021 half hourly data:  

https://data.nationalgrideso.com/demand/historic-demand-data/r/historic_demand_data_2021


```{r}
#V2G80 

library(tidyverse)
library(ggplot2)

library(knitr)
library(xtable)





df_v2g80 <- read_csv("C:/Users/k_gag/OneDrive/Desktop/Dissertation_V2G/results/balancing_80.csv")
#Converting in GW

df_v2g80$demand_80 <- df_v2g80$demand_80*0.001
df_v2g80$solar <- df_v2g80$solar*0.001
df_v2g80$wind <- df_v2g80$wind*0.001
df_v2g80$V2G_80 <- df_v2g80$V2G_80*0.001


mod_v2g80 <- lm(demand_80 ~ solar+wind+V2G_80, data = df_v2g80)
smod_v2g80 <- data.frame(xtable(summary(mod_v2g80)))

```


```{r}
#MonteCarlo Multivariate Regression at 80% V2G occupancy

library(data.table)
m_demand_80 <- mean(df_v2g80$demand_80)
sd_demand_80 <- sd(df_v2g80$demand_80)

m_solar_80 <- mean(df_v2g80$solar)
sd_solar_80 <- sd(df_v2g80$solar)


m_wind_80 <- mean(df_v2g80$wind)
sd_wind_80 <- sd(df_v2g80$wind)


m_v2g_80 <- mean(df_v2g80$V2G_80)
sd_v2g_80 <- sd(df_v2g80$V2G_80)


fit <- lm(demand_80 ~ solar+wind+V2G_80,data =df_v2g80 )
beta_0 = fit$coefficients[1] #Slope  
beta_1 = fit$coefficients[2] # solar
beta_2 = fit$coefficients[3] # wind
beta_3 = fit$coefficients[4] # V2G_80

set.seed(1) #Seed
n = 365*48 # Sample Size
M =  500 # Number of Experiments


#Storage 
slope_DT <- rep(0,M)
slope_DT_2 <- rep(0,M)
intercept_DT <- rep(0,M)



estimates_DT <- do.call("rbind",lapply(1:M, function(i) {
  # Generate data
  U_i = rnorm(n, mean = 47.48, sd = 0) # Error
  X_i_1 = rnorm(n, mean = m_solar_80, sd = sd_solar_80) # First independent variable/solar
  X_i_2 = rnorm(n, mean = m_wind_80, sd = sd_wind_80) #Second independent variable/wind
  X_i_3 = rnorm(n, mean = m_v2g_80, sd = sd_v2g_80) # Third independent variable/v2g_80
  
  Y_i = beta_0 + beta_1*X_i_1 + beta_2*X_i_2 + beta_3*X_i_3 + U_i  # Dependent variable/Obtaining the demand through regression 

  # Formulate data.table
  data_i = data.table(Y = Y_i, X1 = X_i_1, X2 = X_i_2, X3 = X_i_3)
  
  # Run regressions
  ols_i <- fixest::feols(data = data_i, Y ~ X1 + X2 + X3)  
  ols_i$coefficients
}))

estimates_DT_80 <- setNames(data.table(estimates_DT),c("Coeff_intercept","Coeff_Solar","Coeff_Wind","COeff_V2G_80%"))



```



```{r}

#V2G50 

library(tidyverse)
library(ggplot2)

library(knitr)
library(xtable)





df_v2g50 <- read_csv("C:/Users/k_gag/OneDrive/Desktop/Dissertation_V2G/results/balancing_50.csv")
#Converting in GW

df_v2g50$demand_50 <- df_v2g50$demand_50*0.001
df_v2g50$solar <- df_v2g50$solar*0.001
df_v2g50$wind <- df_v2g50$wind*0.001
df_v2g50$v2g_50 <- df_v2g50$v2g_50*0.001


mod_v2g50 <- lm(demand_50 ~ solar+wind+v2g_50, data = df_v2g50)
smod_v2g50 <- data.frame(xtable(summary(mod_v2g50)))




```

```{r}
#MonteCarlo Multivariate Regression at 50% V2G occupancy
library(data.table)

library(data.table)
m_demand_50 <- mean(df_v2g50$demand_50)
sd_demand_50 <- sd(df_v2g50$demand_50)

m_solar_50 <- mean(df_v2g50$solar)
sd_solar_50 <- sd(df_v2g50$solar)


m_wind_50 <- mean(df_v2g50$wind)
sd_wind_50 <- sd(df_v2g50$wind)


m_v2g_50 <- mean(df_v2g50$v2g_50)
sd_v2g_50 <- sd(df_v2g50$v2g_50)


fit <- lm(demand_50 ~ solar+wind+v2g_50,data =df_v2g50 )
beta_0 = fit$coefficients[1] #Slope  
beta_1 = fit$coefficients[2] # solar
beta_2 = fit$coefficients[3] # wind
beta_3 = fit$coefficients[4] # V2G_80

set.seed(1) #Seed
n = 365*48 # Sample Size
M =  500 # Number of Experiments


#Storage 
slope_DT <- rep(0,M)
slope_DT_2 <- rep(0,M)
intercept_DT <- rep(0,M)


estimates_DT <- do.call("rbind",lapply(1:M, function(i) {
  # Generate data
  U_i = rnorm(n, mean = 0.0296, sd = 0) # Error
  X_i_1 = rnorm(n, mean = m_solar_50, sd = sd_solar_50) # First independent variable
  X_i_2 = rnorm(n, mean = m_wind_50, sd = sd_wind_50) # Second independent variable
  X_i_3 = rnorm(n, mean = m_v2g_50, sd = sd_v2g_50) # Third independent variable
  
  Y_i = beta_0 + beta_1*X_i_1 + beta_2*X_i_2 + beta_3*X_i_3 + U_i  # Dependent variable
  # Formulate data.table
  data_i = data.table(Y = Y_i, X1 = X_i_1, X2 = X_i_2, X3 = X_i_3)
  
  # Run regressions
  ols_i <- fixest::feols(data = data_i, Y ~ X1 + X2 + X3)  
  ols_i$coefficients
}))

estimates_DT_50 <- setNames(data.table(estimates_DT),c("Coeff_intercept","Coeff_Solar","Coeff_Wind","Coeff_V2G_50%"))



```


The Vehicle Availiblity function has been obtained through inversing the traffic data and later normalizing the availibity function for utilising  



```{r}

#V2G30 

library(tidyverse)
library(ggplot2)

library(knitr)
library(xtable)





df_v2g30 <- read_csv("C:/Users/k_gag/OneDrive/Desktop/Dissertation_V2G/results/balancing_30.csv")

#Converting in GW:

df_v2g30$demand_30 <- df_v2g30$demand_30*0.001
df_v2g30$solar <- df_v2g30$solar*0.001
df_v2g30$wind <- df_v2g30$wind*0.001
df_v2g30$v2g_30 <- df_v2g30$v2g_30*0.001

#Mulitvariate Linear Regression:

mod_v2g30 <- lm(demand_30 ~ solar+wind+v2g_30, data = df_v2g30)
smod_v2g30 <- data.frame(xtable(summary(mod_v2g30)))




```


```{r}

#MonteCarlo Multivariate Regression at 30% V2G occupancy

library(data.table)
m_demand_30 <- mean(df_v2g30$demand_30)
sd_demand_30 <- sd(df_v2g30$demand_30)

m_solar_30 <- mean(df_v2g30$solar)
sd_solar_30 <- sd(df_v2g30$solar)


m_wind_30 <- mean(df_v2g30$wind)
sd_wind_30 <- sd(df_v2g30$wind)


m_v2g_30 <- mean(df_v2g30$v2g_30)
sd_v2g_30 <- sd(df_v2g30$v2g_30)


fit <- lm(demand_30 ~ solar+wind+v2g_30,data =df_v2g30 )
beta_0 = fit$coefficients[1] #Slope  
beta_1 = fit$coefficients[2] # solar
beta_2 = fit$coefficients[3] # wind
beta_3 = fit$coefficients[4] # V2G_80

set.seed(1) #Seed
n = 365*48 # Sample Size
M =  500 # Number of Experiments


#Storage 
slope_DT <- rep(0,M)
slope_DT_2 <- rep(0,M)
intercept_DT <- rep(0,M)


estimates_DT <- do.call("rbind",lapply(1:M, function(i) {
  # Generate data
  U_i = rnorm(n, mean = 17.78, sd = 0) # Error/obtained through regressing in multivariate format with the demand 
  X_i_1 = rnorm(n, mean = m_solar_30, sd = sd_solar_30) # First independent variable/solar
  X_i_2 = rnorm(n, mean = m_wind_30, sd = sd_wind_30) #Second independent variable/wind
  X_i_3 = rnorm(n, mean = m_v2g_30, sd = sd_v2g_30) # Third independent variable/v2g_30
  
  Y_i = beta_0 + beta_1*X_i_1 + beta_2*X_i_2 + beta_3*X_i_3 + U_i  # Dependent variable

  # Formulate data.table
  data_i = data.table(Y = Y_i, X1 = X_i_1, X2 = X_i_2, X3 = X_i_3)
  
  # Run regressions
  ols_i <- fixest::feols(data = data_i, Y ~ X1 + X2 + X3)  
  ols_i$coefficients
}))

estimates_DT_30 <- setNames(data.table(estimates_DT),c("Coeff_intercept","Coeff_Solar","Coeff_Wind","Coeff_V2G_30%"))

```







